---
title: "Untitled"
author: "Kaylah Marcello"
date: "2/15/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(janitor)
library(skimr)
library(RColorBrewer)
library(paletteer)
library(here)
library("remotes")
library(ggthemes)
```

Predicting cyanobacterial blooms from Tromas et al. 2017 [paper](https://www.nature.com/articles/ismej201758#MOESM502)
```{r}
cyano_bloom <- readr::read_csv("BIS15_dataset.csv")
```
```{r}
cyano_bloom <- clean_names(cyano_bloom)
```

```{r}
glimpse(cyano_bloom)
```

```{r}
summary(cyano_bloom)
```
## Basic stuff: total phosphorus in μg/l (TP), total nitrogen in mg/l (TN), particulate phosphorus in μg/l (PP, the difference between TP and DP), particulate nitrogen in mg/l (PN, the difference between TN and DN), soluble reactive phosphorus in μg/l (DP), dissolved nitrogen in mg/l (DN)
```{r}
cyano_bloom
```

Are blooms during a particular months?
```{r}
c <- cyano_bloom %>% 
  ggplot(aes(x=months, fill=bloom))+
  geom_bar(na.rm=T, position="dodge")
c
```

```{r}
c+theme_classic()+
  theme(axis.text.x = element_text(angle = 60, hjust=1))+
  labs(title = "Bloom During any Particular Month",
       x = NULL,
       y= "sample",
       fill= "Bloom")
```

```{r}
cyano_bloom %>% 
  ggplot(aes(x=years, fill=bloom))+
  geom_bar(na.rm=T, position="dodge")
```

This is me just messing around -Kaylah

