---
title: "Cold Tolerance Gene Variation In Cyanobacteria Over Global Temperature Gradients"
author: "Kaylah Marcello"
date: "2/15/2022"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#install.packages("viridisLite")
```


##Load the Libraries

```{r}
library(tidyverse)
library(RColorBrewer)
library(paletteer)
library(janitor)
library(here)
library(skimr)
library(viridis)
library(shiny)
library(shinydashboard)
library(devtools)
```

```{r}
filament_cyanos <- readr::read_csv("data/filamentous_cyano_meta.csv")
```
## Get an Idea of the Structure
```{r}
summary(filament_cyanos)
```

```{r}
head(filament_cyanos)
```

```{r}
filament_cyanos <- clean_names(filament_cyanos)
```

```{r}
names(filament_cyanos)
```
## Cold Tolerance Gene Counts by Genus and Specific Strain
#make a heat map out of this and maybe a shiny app?
```{r}
gene_data_genus <- filament_cyanos %>% 
  select(genus, contains("gene_")) %>% 
  pivot_longer(-genus,
               names_to = "gene",
               values_to = "gene_count") %>% 
  filter(!is.na(gene_count))
gene_data_genus
```

```{r}
gene_data_genus$gene_count <- as.factor(gene_data_genus$gene_count)
```

```{r}
fil_heatmap <- gene_data_genus %>%
  ggplot(aes(y=gene, x=genus))+
  geom_tile(aes(fill= gene_count, color="white"))+
  scale_fill_viridis(discrete=TRUE, direction = -1)+
  theme(legend.position = "right",
        text = element_text(size=6),
        axis.text.x = element_text(angle = 45, hjust=1))+
  coord_fixed()+ #maintains aspect ratio so 1 unit on x is 1 unit on y
  labs(title = "Cold Tolerance Gene Count for Cyanobacteria Genera",x = "Genome", y = "Gene")

ggsave("figures/fil_gene_count_genus_heatmap.png", width=10, height=6, plot = fil_heatmap, dpi = 200)

fil_heatmap 
```

```{r}
gene_data_organism <- filament_cyanos %>% 
  select(organism, contains("gene_")) %>% # get rid of the gene_ part for the final pres.
  pivot_longer(-organism,
               names_to = "gene",
               values_to = "gene_count") %>% 
  filter(!is.na(gene_count))
gene_data_organism
```

```{r}
gene_data_organism$gene_count <- as.factor(gene_data_organism$gene_count)
```


```{r}
fil_heatmap <- gene_data_organism %>%
  ggplot(aes(y=gene, x=organism))+
  geom_tile(aes(fill= gene_count, color="white"))+
  scale_fill_viridis(discrete=TRUE, direction = -1)+
  theme(legend.position = "right",
        text = element_text(size=6),
        axis.text.x = element_text(angle = 60, hjust=1))+
  coord_fixed()+ #maintains aspect ratio so 1 unit on x is 1 unit on y
  labs(title = "Cold Tolerance Gene Count for Cyanobacteria Strains",x = "Genome", y = "Gene")

ggsave("figures/fil_gene_count_heatmap.png", width=10, height=6, plot = fil_heatmap, dpi = 200)

fil_heatmap 
```

## Cyanobacteria Strain Environmental Temperatures

```{r}
temperature_gene <- filament_cyanos %>% 
  select(organism, tempurature_avg, contains("gene_")) %>% 
  filter(!is.na(tempurature_avg))
temperature_gene
```

```{r}
temp_organism <- filament_cyanos %>% 
  select(organism, tempurature_avg, genus) %>% 
  filter(!is.na(tempurature_avg)) %>% 
  ggplot(aes(x = organism, y = tempurature_avg, fill = genus)) +
  geom_col()+
  theme(legend.position = "right",
        text = element_text(size=7),
        axis.text.x = element_text(angle = 60, hjust=1))+
  labs(title = "Environmental Temperature for Cyanobacteria Species",x = "Cyanobacteria", y = "Temperature C")
temp_organism
ggsave("figures/temp_organism_plot.png", width=10, height=6, plot = temp_organism, dpi = 200)


```

## Compare single gene count to temperature in previouse figure

```{r}
#this one would be good for the shiny app bc you could change out each gene.
temp_organism <- filament_cyanos %>% 
  select(organism, tempurature_avg, genus, gene_gyr_a) %>% 
  filter(!is.na(tempurature_avg)) %>% 
  filter(!is.na(gene_gyr_a)) %>% 
  ggplot(aes(x = organism, y = gene_gyr_a, fill = genus)) +
  geom_col()+
  theme(legend.position = "right",
        text = element_text(size=6),
        axis.text.x = element_text(angle = 60, hjust=1))+
  labs(title = "CTG count for Cyanobacteria Species",x = "Cyanobacteria", y = "Gene Count")

ggsave("figures/fil_gene_plot.png", width=10, height=6, plot = temp_organism, dpi = 200)

temp_organism
```


#join function information at some point
#filter out just the cold environment species and look at gene variation in them
